\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
%\usepackage[scale=0.93]{geometry}
\usepackage[
  scale  = 0.93,
  top    = 1.0cm,
  bottom = 0.50cm,
  left   = 1.0cm,
  right  = 1.0cm]{geometry}

\setlength{\hintscolumnwidth}{2.0cm}

\newcommand\myitem{\item[\textbullet] }

\AtBeginDocument{\recomputelengths}

% personal data
\firstname{Adrien}
\familyname{Conrath~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}
\address{9 rue Pierre Bizos}{92330 Sceaux, France}
\mobile{+33(0)650.836.384} % TODO: change with american number
\email{adrienconrath@gmail.com}

\begin{document}
\maketitle

%----------------------------------------------------------------------------------
%            Work experience
%----------------------------------------------------------------------------------

\section{Work Experience}

\cventry{Feb 2013 - Aug 2013}{Software Engineer Intern}{Nvidia
(USA)}{}{}{Develop \textbf{debugging and profiling} tool targeting Nvidia's next generation \textbf{Tegra 5} for graphic applications.\newline
  - \underline{Main mission}: Work on cross-platform core messaging system, \textbf{C++, Networking, Asynchronous I/O};\newline
  - Integrate \textbf{Android build system} to existing \textbf{CMake} environment;\newline % TODO: 'integrate'
  - Design and implement \textbf{back-end for crash reporting solution} based on Google
  Breakpad, \textbf{PostgreSQL, PHP, Perl}.
}

\cventry{Aug 2012 - Jan 2013}{System Administrator}{Epita (France)}{}{}{
    Maintain teaching team's computer lab in operational condition. Network and
    security management. Provide services for 300 students and 30 teaching
    assistants including: git, mercurial, mailing-lists, Intranet.
    \newline \underline{Main mission}: Develop distributed automated test engine for correcting students' projects.
  }
\cventry{Jan 2012 - Jan 2013}{Teaching Assistant}{}{Epita (France)}{}{
  Member of the teaching team for first year engineering students.
  Redacting and correcting practicals and exams, conducting practicals.
  \textbf{C, C++, Java, PostgreSQL, Linux}.}
\cventry{2011}{Software Engineer Intern}{Spheris Digital Ltd.}{Beijing (China)}{}{
  Develop and administrate back-end platform for connected digital picture frames.\newline
  - Picture and video processing. Resizing, Thumbnail Creation, Video Encoding.\newline
  - Synchronization with external providers (Facebook, Picasa, Flickr, Skydrive, \ldots).
}
\cventry{2010}{Teaching Assistant}{}{Epita (France)}{}{Teaching assistant for a
class of 40 students. \textbf{Ocaml, C\#}.}
\cventry{2010}{Web Developer Intern}{Epita (France)}{}{}{Develop Intranet
  website for students. Implement form generation and statistics tools in a team of 4
developers.}

%----------------------------------------------------------------------------------
%            Education
%----------------------------------------------------------------------------------

\section{Education}

\cventry{Sept 2013}{Computer Engineering Degree}{Epita (France)}{Computer Engineering and Real-Time Embedded Systems}{}{%
  \textbf{Algorithms}, \textbf{Software Design}, \textbf{Object Oriented
  Design}, \textbf{Operating Systems}, \textbf{Databases}, \textbf{Compiler
  Construction}, \textbf{TCP/IP}, Mathematics, Formal Language Theory, Kernel
  Programming, Microprocessors, Parallel Programming, Linux module programming,
Windows CE / RTX, Electronics, Control Engineering.}
\cventry{2011}{Beijing}{Took Mandarin Chinese private lessons during 5 months internship}{}{}{}
\cventry{2010}{International Semester}{Shanghai JiaoTong University}{Shanghai (China)}{\newline Semester abroad courses: Chinese, intro to Artificial Intelligence, Embedded Systems, Electronics and C++}{}

%----------------------------------------------------------------------------------
%            Languages and Technologies
%----------------------------------------------------------------------------------

\section{Languages and Technologies}
\cvline{Languages}{\textbf{C}; \textbf{C++}; \textbf{Shell scripting}; \textbf{Perl}; \textbf{Java}; \textbf{PHP}; \textbf{SQL (PostgreSQL, MySQL)}; JavaScript; C\#; ASM; Caml.}
\cvline{Technologies}{\textbf{Networking}, \textbf{Asynchronous I/O}, \textbf{Git}, \textbf{Perforce}, \textbf{CMake}, \LaTeX, Intel TBB.}
\cvline{Systems}{\textbf{Android}, \textbf{Linux}, \textbf{Linux System Administration.}}

%----------------------------------------------------------------------------------
%            Main IT projects
%----------------------------------------------------------------------------------

\section{Programming projects}
\cventry{2013}{Collaborative school project with Thales (France)}{
  Develop an API that processes and shares data from sensors such as
GPS, and Gyrometer on board computers. Display connected devices on OpenStreetMap maps}{}{}{}
\cventry{2012}{Intel Acceler8 Contest}{Optimize and parallelize a reference algorithm}{}{}{}
\cventry{2012}{Educational micro-kernel in C}{Bootloader in Assembly,
  Interrupts Management, Paging, Context Switching and Scheduling Algorithm}{1 month}{}{}
\cventry{2011}{POSIX Shell developed in C}{1 month. Team of 5. Highest rank}{}{}{}
\cventry{2011}{Compiler developed in C++}{Compiler for the Tiger language,
  front-end and back-end: Lexer, Parser, AST Construction, Binding, Type
Checker, Instruction Selection, Liveness Analysis and Register Allocation}{}{}{}
\cventry{2011}{Design and develop Virtual Machine and Assembler}{Team of 5. Highest rank}{}{}{}
\cventry{2009}{Video game in Delphi}{Develop physics engine of a
  video game based on the ``Worms'' concept, team of 4 people. Highest rank.
\underline{Performed demonstration at The Paris Video Games Festival}}{}{}{}
\cventry{Other}{``Reiventing the wheel''}{Implementation of \textbf{Make},
\textbf{malloc}, \textbf{HTTP server}, \textbf{C standard IO library}, compliant with existing tools}{}{}{}

%----------------------------------------------------------------------------------
%            Languages
%----------------------------------------------------------------------------------

\section{Languages}
\cvdoubleitem{French}{Native}{English}{Bilingual proficiency}
\cvdoubleitem{Chinese}{Moderate}{Spanish}{School level}

\end{document}
